\bf On semidefinite-representable sets over valuation fields

### 2025-05-17 article/paper_padic_spec.tex
correctness

\begin{algorithm}
    \caption{\textbf{SOLVELPval}($A,b,c,D,e$)}\label{algo_LP}
    \begin{algorithmic}[1]
      \REQUIRE
      $A \in K^{d\times n}$, $b \in K^d$, $c \in K^n$, $D \in K^{m \times n}$ and $e \in K^m$
      \ENSURE [TYPE, $x$], where:
      \vspace{-0.25cm}
      \begin{itemize}
      \item[]
        TYPE $=$ INFEAS and $x=[]$ if and only if \eqref{LP} is infeasible
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ UNBOUND and $x=[]$ if and only if \eqref{LP} is feasible and unbounded
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ FEAS if and only if \eqref{LP} is feasible and has a solution $x$
      \end{itemize}
      \vspace{-0.1cm}
      \hrule
      \vspace{0.1cm}
      \IF{$Dx = e$ has no solution}
      \RETURN [INFEAS, []]
      \ENDIF
      \IF{$D \neq {\bf 0}$}
      \STATE find $J \in K^{n \times R}$, with $R = \dim\ker D$, such that $\text{Im}\, J = \ker D$
      \STATE find $x_0$ such that $Dx_0=e$
      \RETURN $\textbf{SOLVELPval}(AJ,b+A x_0,J^T c, {\bf 0},0)$ \hfill {\color{olive} \# \Cref{reducD}}
      \ENDIF
      \IF{$A$ not in Smith Normal Form}
      \STATE $[Q,S,P] \leftarrow \textbf{SNF}(A)$
      \STATE $[\mathrm{STATUS}, y] \leftarrow \textbf{SOLVELPval}(S,Qb,(P^{-1})^Tc,{\bf 0},0)$
      \RETURN $[\mathrm{STATUS}, P^{-1}y]$ \hfill {\color{olive} \# \Cref{solsLP}}
      \ELSE
      \STATE $r \leftarrow \text{rank}(A)$
      \IF{$\bigwedge_{i=r+1}^d \val(b_{i}) \geq 0$}
      \STATE STATUS $\leftarrow$ FEAS
      \STATE give solution in this case
      \ELSE
      \STATE
      \STATE
      \RETURN ... \hfill {\color{olive} \# \Cref{prop:reduc}}
      \ENDIF
      \ENDIF
    \end{algorithmic}
\end{algorithm}

@@

Solving the diagonal \eqref{LP} consists -- by definition -- in minimizing the linear map $y \mapsto \val\left(\left\langle
c',y \right\rangle\right)$ over $\PP'$. The image of $\PP'$ by $y \mapsto \left\langle c',y \right\rangle$ is
\[
\left\langle c',\PP' \right\rangle = \sum_{i=1}^r -c'_i \frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right) = \lambda + \pi^{v} \OK
\]
where $\lambda = \sum_{i=1}^r -c'_i \frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.

Two cases can occur depending on $v$ and the valuation of $\lambda$.
If $\val(\lambda) < v$, the minimum of $y\mapsto \val\left(\left\langle c',y \right\rangle\right)$ over $\PP'$
  is reached at any point of $\PP'$, and is equal to $\val(\lambda)$.
  Otherwise, if $\val(\lambda) \ge v$, then $\lambda \in \pi^{v} \OK$ and the minimum is $v$ and is reached at any points $y$
  of $\PP'$ such that $\left<c',y \right> \in \pi^v$.

  We conclude with a correctness theorem.

  \begin{theorem} \Cref{algo_LP} is correct.
  \end{theorem}
  \begin{proof}
  \end{proof}

>>>>

\begin{algorithm}
    \caption{\textbf{SOLVELPval}($A,b,c,D,e$)}\label{algo_LP}
    \begin{algorithmic}[1]
      \REQUIRE
      $A \in K^{d\times n}$, $b \in K^d$, $c \in K^n$, $D \in K^{m \times n}$ and $e \in K^m$
      \ENSURE [TYPE, $x$], where:
      \vspace{-0.25cm}
      \begin{itemize}
      \item[]
        TYPE $=$ INFEAS and $x=[]$ if and only if \eqref{LP} is infeasible
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ UNBOUND and $x=[]$ if and only if \eqref{LP} is feasible and unbounded
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ FEAS if and only if \eqref{LP} is feasible and has a solution $x$
      \end{itemize}
      \vspace{-0.1cm}
      \hrule
      \vspace{0.1cm}
      \IF{$Dx = e$ has no solution}
        \RETURN [INFEAS, []] \label{step:linear_empty}
      \ENDIF
      \IF{$D \neq {\bf 0}$} \label{step:reducD:begin}
        \STATE find $J \in K^{n \times R}$, with $R = \dim\ker D$, such that $\text{Im}\, J = \ker D$
        \STATE find $x_0$ such that $Dx_0=e$ \label{step:reducD:end}
        \RETURN $\textbf{SOLVELPval}(AJ,b+A x_0,J^T c, {\bf 0},0)$ \label{step:reducD} \hfill {\color{olive} \# \Cref{reducD}}
      \ENDIF
      \IF{$A$ not in Smith Normal Form} \label{step:solsLP:begin}
        \STATE $[Q,S,P] \leftarrow \textbf{SNF}(A)$
        \STATE $[\mathrm{STATUS}, y] \leftarrow \textbf{SOLVELPval}(S,Qb,(P^{-1})^Tc,{\bf 0},0)$ \label{step:solsLP:end}
        \RETURN $[\mathrm{STATUS}, P^{-1}y]$ \hfill {\color{olive} \# \Cref{solsLP}} \label{step:solsLP}
      \ENDIF
      \STATE $r \leftarrow \text{rank}(A)$ \label{step:core:begin}
      \IF{$\bigwedge_{i=r+1}^d \val(b_{i}) \geq 0$}
        \IF{$\bigvee_{i=r+1}^n c_i \neq 0$}
        \RETURN [UNBOUND, []] \hfill {\color{olive} \# \Cref{prop:reduc}, item \ref{prop:reduc_it2}}
        \ELSE
          %\STATE STATUS $\leftarrow$ FEAS
          \STATE $\lambda \leftarrow -\sum_{i=1}^r c_i b_i / s_i$
          \STATE $v \leftarrow \min_{1 \leq i \leq r} \val (c_i/s_i)$
          \IF{$\val \lambda < v$}
            \STATE choose $y \in K^n$ such that $y_i \in (-b_i+\OK)/s_i, i=1,\ldots,r$
            \RETURN [FEAS, $y$]
          \ELSE
            \STATE find $y \in K^n$ such that $y_i \in (-b_i+\OK)/s_i, i=1,\ldots,r$
            and $\langle c,y\rangle = \pi^v\OK$
            \RETURN [FEAS, $y$]
          \ENDIF
        \ENDIF 
      \ENDIF
        %\STATE
        %\STATE
        %\RETURN ... \hfill {\color{olive} \# \Cref{prop:reduc}}
      %\ENDIF \label{step:core:end}
      \RETURN [INFEAS, []]
    \end{algorithmic}
\end{algorithm}

@@

Solving the diagonal \eqref{LP} consists -- by definition -- in minimizing the linear map $y \mapsto \val\left(\left\langle
c',y \right\rangle\right)$ over $\PP'$. The image of $\PP'$ by $y \mapsto \left\langle c',y \right\rangle$ is
\[
\left\langle c',\PP' \right\rangle = \sum_{i=1}^r -c'_i \frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right) = \lambda + \pi^{v} \OK
\]
where $\lambda = -\sum_{i=1}^r c'_i \frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.

Two cases can occur depending on $v$ and the valuation of $\lambda$.
If $\val(\lambda) < v$, the minimum of $y\mapsto \val\left(\left\langle c',y \right\rangle\right)$ over $\PP'$ is reached at any point of $\PP'$, and is equal to $\val(\lambda)$.
Otherwise, if $\val(\lambda) \ge v$, then $\lambda \in \pi^{v} \OK$ and the minimum is $v$ and is reached at any points $y$ of $\PP'$ such that\footnote{\simone{J'imagine que c'est plutôt
$\left<c',y \right> \in \pi^v\OK$ ?}} $\left<c',y \right> \in \pi^v$.

We conclude with a correctness theorem for \Cref{algo_LP}.

  \begin{theorem} \Cref{algo_LP} is correct.
  \end{theorem}
  \begin{proof}
    If the linear system $Dx=e$, Problem \eqref{LP} is infeasible
    and \Cref{algo_LP} outputs correct answer at step \ref{step:linear_empty}.
    Else, by \Cref{reducD} the input problem can be reduced to a new linear
    program with $D={\bf 0}$ and $e=0$, which is done at steps
    \ref{step:reducD:begin}-\ref{step:reducD:end},
    and the correct output is given at step \ref{step:reducD}.
    The reduction based on SNF from \Cref{solsLP} is performed at
    steps \ref{step:solsLP:begin}-\ref{step:solsLP:end} and the output
    is given at step \ref{step:solsLP}.

    The core of \Cref{algo_LP} is on steps \ref{step:core:begin}-\ref{step:core:end}.

    TO BE CONTINUED.
  \end{proof}
